### 2019-04-24 appendices/proofs.tex
rename main tex file to main
shorten proofs section

@@

>>>>

\begin{lemma}[Task value preserves types]
  % For all well typed expressions $e$ and states $\sigma$,
  For all expressions $e$ and states $\sigma$
  such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Sigma \infers \sigma$,
  if $\Value{(e,\sigma)}=v$,
  then $v:\tau$.
  \label{lem:presvalue}
\end{lemma}

@@

\begin{lemma}[Striding preserves types]
  For all expressions $e$ and states $\sigma$
  such that $\Gamma,\Sigma \infers e:\Task\tau$ and $\Sigma \infers \sigma$,
  if $e,\sigma \stride e',\sigma'$,
  then $\Gamma,\Sigma \infers e':\Task\tau$ and $\Sigma \infers \sigma'$.
  \label{thm:pres-stride}
\end{lemma}
